---
title: "Assignment_9"
author: "Preston Lines"
date: "2022-11-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r include=FALSE}
library(tidyverse)
library(modelr)
library(GGally)
library(easystats)
library(broom)
```

load the file
```{r echo=TRUE, results='hide'}
read_csv(file = "GradSchool_Admissions.csv")
```

save it as a dataframe
```{r echo=TRUE, results='hide'}
df <- read_csv(file = "GradSchool_Admissions.csv")
```

see some general correlations between the columns
```{r echo=TRUE, results='hide'}
df %>% 
  select(admit,gre,gpa,rank) %>% 
  ggpairs()
```

observe how the GRE scores and the gpa affect admission
```{r echo=TRUE}
df %>% 
  ggplot(aes(x = gre,y = gpa)) +
  facet_wrap(~admit) +
  geom_point()
```

very interesting results, some students have very high GRE scores and GPA but were not admitted
let's analyze the rank of their undergraduate studies
```{r echo=TRUE, results='hide'}
df %>% 
  ggplot(aes(x = gre,fill = admit)) +
  facet_grid(admit~rank) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90))
```

let's plot the exact same data but with GPA instead of GRE scores
```{r echo=TRUE, results='hide'}
df %>% 
  ggplot(aes(x = gpa,fill = admit)) +
  geom_density(alpha=0.5) +
  facet_grid(admit~rank) +
  theme(axis.text.x = element_text(angle = 90))
```

plot everything we've learned into one plot, showing gre, gpa, rank, and admission
```{r echo=TRUE, results='hide'}
df %>% 
  ggplot(mapping = aes(x = gre, y=gpa, color=rank))+
  geom_point()+geom_smooth(aes(sd(FALSE)))
```

make a model of the rank of the undergraduate institution factoring in gre and gpa
```{r echo=TRUE, results='hide'}
mod1 <- glm(data = df,formula = rank ~ gre + gpa)
```

create a second model, this time showing admissions by gre and gpa
```{r echo=TRUE, results='hide'}
mod2 <- glm(data = df,formula = admit ~ gre + gpa)
```

create mod3 using stepAIC
```{r echo=TRUE, results='hide'}
fullmod <- glm(data = df,formula = admit ~ gre + gpa + rank)
step <- MASS::stepAIC(fullmod, trace=0)
mod3 <- glm(data = df,formula = step$formula)
```

make a prediction function
```{r echo=TRUE, results='hide'}
df %>%
  gather_predictions(mod1,mod2,mod3) %>%
  ggplot(aes(x = gpa, y = pred, color=model))+
  geom_segment(aes(x = 0,y = 0,xend=4, yend=4),linetype=2,
               color="black",alpha=.5)+
  geom_smooth(method = "lm",se=FALSE)+
  facet_wrap(~admit)
```

it's a bit off, but I tried my best :)

