---
title: "LINES_Skills_Test_3.R"
author: "Preston Lines"
date: "2022-11-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


```{r include=FALSE}
library(tidyverse)
library(patchwork)
library(janitor)
library(easystats)
library(modelr)
library(broom)
```


## Task 1

I started by loading the .csv files

```{r echo=TRUE, results='hide'}
money <- read_csv(file = "FacultySalaries_1995.csv")

oil <- read_csv(file = "Juniper_Oils.csv")
```

Tidying the data for plotting purposes, using pivot_longer

```{r}
money1 <-
  pivot_longer(money, 5:17, names_to = "Observation", values_to = "Total")
```

First Plot 

```{r}
money1 %>% filter(grepl('Salary', Observation)) %>%
  filter(!grepl('AvgProfSalaryAll', Observation)) %>%
  filter(!grepl('VIIB', Tier)) %>%
  ggplot(mapping = aes(y = Total,fill = Observation))+
  geom_boxplot()+facet_grid(~Tier)+theme_minimal()+
  scale_fill_discrete(name = "Rank", labels = c("Assist", "Assoc", "Full")) +
  labs(y = "Salary",x = "Rank") +theme(axis.text.x = element_text(angle = 45))
```

Save that plot as p1

## Task 2, Build an ANOVA model and display the summary output in your report.
let's modify the money data set to build an ANOVA model

```{r}
money <- pivot_longer(money,contains("Salary"),
                      names_to = "Rank_Salary",
                      values_to = "Salary")
```

Add an ANOVA model

```{r}
aov(money,formula = money$Salary ~
      money$Tier+money$Rank_Salary+money$State)
```

## Task 3, tidy the Juniper_Oils data set

```{r}
oil <- pivot_longer(oil, 11:33, names_to = "ChemicalID")
```

## Task 4, the chemicals plot

```{r}
oil %>% 
  ggplot(mapping = aes(x = YearsSinceBurn,y = value)) +
  geom_smooth(method = "loess") +
  facet_wrap(~ChemicalID, scales = "free") +
  theme_minimal() +
  labs(y = "Concentration")
```

Let's call this p2

## Task 5, create a GLM of the data 

```{r}
mod1 <- glm(formula=oil$Yield_percent~
              oil$YearsSinceBurn)
```

Tidy it to find only those that are significant

```{r}
tidy(mod1) %>%
  filter(p.value< 0.05)
```


